---
title: Soybean Deliveries
author: Pablo Figueroa
date: '2017-09-19'
slug: soybean-deliveries
categories:
  - Soybeans
tags:
  - Crush
  - Deliveries
  - Trucks
---

```{r,include=FALSE}
library(vtreat)
library(ISLR)
library(readxl)
library(forecast)
library(ggplot2)
library(xlsx)
library(xts)
library(leaps)
library(MASS)
library(glmulti)
library(HH)
library(glmnet)
library(pls)
library(broom)
library(tidyr)
library(dplyr)
library(data.table)
```

#Summary
Below, another attempt to model crush using **Subset Selection, Shrinkage and Dimension Reduction** to fit different models using a determined set of variables. 
This models were selected based on R-adjusted and Cp and then Cross-Validated to have an idea of the prediction power of the models and expected errors.

## Ideas for the future/line of work derived from this:

Models could be improved if a series of deliveries was considered, but we don´t have this estimate before official crush is published. From this we can derive the importance of having a goo estimate of deliveries, based not only on truck arrivals but farmer selling to estimate both crush and physical stocks.
Im not adding a variable to acount for working days of each month. Indirectly this may be accounted through the month as a seasonal component (some months are includded in the best model which has 13 variables)
would be good to include a variable to account for loading pace during the first days of the following month. this can be included though SBM_fwd exports but we can add only loded volumnes during 10/15 days. Another possibility is adding loaded % of total exports during the first 10/15 days.

#Conclusion:
Best model found is the one includding xx variables yielding and error or xx.

Data Subset includidng variables for which we have the data before official estimate is pusblished

##Description of the data set:


```{r, include=F,warning=FALSE,echo=FALSE}
# Load Data
data<-read_excel("C:/Users/figuerpa/ShareFile/Shared With Me/OFFICE/ARGENTINA/COMMERCIAL DATA/CRUSH/R_Project/Crush_Model/Data.xlsx","Data4")

#Set Parameters
last_col=ncol(data)

# Create XTS and separate data
newdata<-data[,1:last_col-1]

data_train<-na.omit(subset(data,data$Estimate=="No"))

data_train<-data_train[,1:last_col-1]

data_test<-subset(data,data$Estimate=="Yes")
data_ts<-ts(data,start = c(2001),frequency = 1)[,1:last_col]
train_ts<-ts(data_train,start = c(2009,4),frequency = 12)[,3:last_col-1]
#test_ts<-ts(data_test,start = c(2018,5),frequency = 1)[,1:last_col-1]
```





#Exploratory Analysis and graphs

```{r, echo=FALSE}

data_train_mut<-mutate(data_train,Month=months(data_train$Date))
data_train_mut<-mutate(data_train_mut,Year=year(data_train$Date))

par(mfrow=c(1,3))
ggplot(data=data_train_mut,aes(x=Truck_Crushers,y=Crush,color=Month))+geom_point()+geom_jitter()+geom_smooth(method = "loess", aes(group=1))

ggplot(data=data_train_mut,aes(x=Truck_Crushers,y=Crush,color=factor(Year)))+geom_point(alpha=0.4)+
  geom_smooth(method = "lm",se=0)+geom_smooth(aes(group=1),method = "lm",se=F,linetype=2,col="red")

#ggplot(data=data_train_mut,aes(x=Truck_Crushers,y=Crush,color=factor(Year)))+ geom_smooth(method = "lm",se=0)+geom_smooth(aes(group=1),method = "lm",se=F,linetype=2,col="red")

```